Objective-first optimization for nanophotonics

### 2011-08-04 presentations/ob1_aug-2011/objective-first.tex
Re-organized and finalized ob-1 presentation.

\BIT
\item key issue: formulation of the constraint
\item a sufficient constraint for most devices is to match field values along the border
\BEQ f(x) = \| x^\text{border} - x^\text{border}_0 \|^2 = 0 \EEQ
\begin{center}
\includegraphics[width=0.8\textwidth]{../figures/waveguide.jpg}
\end{center}
\item here, $p$ is a waveguide structure, and the design objective is a perfect waveguide mode at input and output
\EIT
\newpage

\BIT
\item to experiment, we fix $p = p_0$, which convexifies the ob-1 formulation
\begin{align}
\mbox{minimize} & \quad \|A(p_0)x\|^2 \\
\subjectto & \quad x^\text{border} = x^\text{border}_0
\end{align}
\item for general structures and design objectives, this results in a ``soft physics'' field solve
\begin{center}
\includegraphics[width=0.8\textwidth]{../figures/crossbar.jpg}
\end{center}
\EIT
\newpage

\BIT
\item prioritizing the design objective means we allow physics to be ``bent''
\item here, reflected waves from the junction magically disappear as they approach the border
\begin{center}
\includegraphics[width=0.8\textwidth]{../figures/mode_converter.jpg}
\end{center}
\item matlab files available at \url{https://github.com/JesseLu/wave-tools}, look for \texttt{em\_bval\_2dte/demo.m}
\EIT

@@

\BIT
\item need ability to \emph{incrementally} update the topology of the structure
\item describe $p$ using the \emph{interface} between the two materials
\item implicitly describe boundary using the \emph{level-set} of higher-dimensional function $\phi$
\begin{center}
\includegraphics[width=0.45\textwidth]{../figures/level-set.jpg} \\
source: public domain
\end{center}
\EIT
\newpage

@@

\BIT
\item to test, hold $x$ constant, and update $p$ (iterations 0, 5, 10, 15, 20 shown)
\begin{center}
\includegraphics[width=0.5\textwidth]{../figures/structure-progression.jpg} \\
\end{center}
\item code at \url{https://github.com/JesseLu/level-set} (\texttt{demo\_indep\_levelset.m})
\item new code at \url{https://github.com/JesseLu/lset-opt}
\EIT

\oursection{Example}
put it all together and let'er rip!

>>>>

\BIT
\item key issue: formulation of the constraint
\item a sufficient constraint for most devices is to match field values along the border
\BEQ f(x) = \| x^\text{border} - x^\text{border}_0 \|^2 = 0 \EEQ
\begin{center}
\includegraphics[width=0.8\textwidth]{figures/waveguide.jpg}
\end{center}
\item here, $p$ is a waveguide structure, and the design objective is a perfect waveguide mode at input and output
\EIT
\newpage

\BIT
\item to experiment, we fix $p = p_0$, which convexifies the ob-1 formulation
\begin{align}
\mbox{minimize} & \quad \|A(p_0)x\|^2 \\
\subjectto & \quad x^\text{border} = x^\text{border}_0
\end{align}
\item for general structures and design objectives, this results in a ``soft physics'' field solve
\begin{center}
\includegraphics[width=0.8\textwidth]{figures/crossbar.jpg}
\end{center}
\EIT
\newpage

\BIT
\item prioritizing the design objective means we allow physics to be ``bent''
\item here, reflected waves from the junction magically disappear as they approach the border
\begin{center}
\includegraphics[width=0.8\textwidth]{figures/mode_converter.jpg}
\end{center}
\item matlab files available at \url{https://github.com/JesseLu/wave-tools}, look for \texttt{em\_bval\_2dte/demo.m}
\EIT

@@

\BIT
\item need ability to \emph{incrementally} update the topology of the structure
\item describe $p$ using the \emph{interface} between the two materials
\item implicitly describe boundary using the \emph{level-set} of higher-dimensional function $\phi$
\begin{center}
\includegraphics[width=0.45\textwidth]{figures/level-set.jpg} \\
source: public domain
\end{center}
\EIT
\newpage

@@

\BIT
\item to test, hold $x$ constant, and update $p$ (iterations 0, 5, 10, 15, 20 shown)
\begin{center}
\includegraphics[width=0.5\textwidth]{figures/structure-progression.jpg} 
\end{center}
\item code at \url{https://github.com/JesseLu/level-set} (\texttt{demo\_indep\_levelset.m})
\item new code at \url{https://github.com/JesseLu/lset-opt}
\EIT

\oursection{Example}
\BIT
\item alternately update $x$, then $p$
\begin{align}
\mbox{decrease} & \quad \|g(x,p)\|^2 \\
\subjectto & \quad f(x) = 0 \\
        & \quad p \in \{p_\text{level-set}\}
\end{align}
\item test on a simple, 2D example on a $30\times30$ grid
\item 10,000 iterations take 3 minutes in Matlab
\item code at \url{https://github.com/JesseLu/objective-first}, look for \texttt{demo\_alternate\_levelset.m}
\EIT
\newpage

\begin{center}
\includegraphics[width=0.7\textwidth]{figures/example.jpg} 
\end{center}
\BIT
\item initial checker-board structure allows for islands to be formed
\EIT
\newpage

\BIT
\item verify by inserting into larger grid with absorbing boundaries, and excite waveguide mode
\begin{center}
\includegraphics[width=0.7\textwidth]{figures/verify.jpg} 
\end{center}
\item slightly more power transmitted than reflected, a lot of room for improvement
\EIT

\oursection{Ongoing and future work}
\BIT
\item currently working out some kinks in level-set code which cause the structure update to ``jam''
\EIT

Next milestones:
\BIT
\item successful waveguide converters in 2D
\item multi-wavelength waveguide devices in 2D
\item implement in 3D, on multi-GPU system
\EIT
